### 2014-10-27 ThesisJo/derivations.tex
la2pdf commit - 2014:10:27	16:25:27	(Mon27.Oct)
la2pdf commit - 2014:10:27	17:00:34	(Mon27.Oct)
la2pdf commit - 2014:10:27	17:39:25	(Mon27.Oct)
More on wave equation

The wave equation describes how a wave move as a function of both time and space. Its importance and application is great, so we will spend some time to derive it here. We will treat acoustical waves since they are most relevant to the topic in this thesis, but we could have derived it from electromagnetic waves using Maxwells equations with some boundary conditions.

Define a small volumetric element $dV = dx dy dz$. 
\begin{wraptable}{r}{8.9cm}%\normalsize
\begin{tabular}[c]{c c l}\hline
\rowcolor{tabBlue}\bf Symbol & \bf Unit & \bf Description \\\hline
$p$ & Pa = N/m$^2$ & Pressure \\
$\rho$ & kg/m$^3$ & Density \\
$S$ &  & Entropy \\
$\vec v$ & m/s & Mass velocity \\
$\dot m$ & kg/s & Mass flow
\end{tabular}
\end{wraptable}%

>>>>

The wave equation describes how a wave move as a function of both time and space. It forms the basis for all mathematical modeling of waves, so we will spend some time to derive it here. We will treat acoustical waves since they are most relevant to the topic in this thesis, but we could have derived it from electromagnetic waves using Maxwells equations with some boundary conditions.

\begin{figure}[ht]
\begin{floatrow}

\floatbox{figure}[\linewidth][\FBheight][t]{%
\caption{Mass flow}}{%
\graphicsAI[drawing,width=.77\linewidth]{gfx/wave_equation_mass_flow.svg}}%

\floatbox{table}[\linewidth][\FBheight][t]{%
\caption{Symbol description}}{%
\begin{tabular}[c]{c c l}\hline
\rowcolor{tabBlue}\bf Symbol & \bf Unit & \bf Description \\\hline
$p$ & Pa = N/m$^2$ & Pressure \\
$\rho$ & kg/m$^3$ & Density \\
$S$ &  & Entropy \\
$\vec v$ & m/s & Mass velocity \\
$\dot m$ & kg/s & Mass flow
\end{tabular}}

\end{floatrow}
\end{figure}

We begin by defining the mass flow in and out of a volumetric element $dV = dx dy dz$:

\begin{align}
\dot m_\text{in} = \rho\,\v\,dV \qquad\qquad \text{and} \qquad\qquad \dot m_\text{out} = \rho\,\v\,dV + 
\end{align}
